\begin{abstract}
Subnational microsimulation needs survey microdata that reproduce administrative totals across
nested geographies while staying usable inside a policy model. A pipeline built for fidelity can
combine many data sources and add record-level variation, which produces a candidate dataset that
is rich enough to represent the variation the targets describe and also large enough to be expensive
to store, calibrate, and simulate. That dataset has to be reduced to a workable size, and the
question is which records to keep.

We study this reduction as a sampling problem. Using $L_0$ regularization with the Hard Concrete
relaxation of \citet{louizos2018}, the method jointly selects which records to retain and assigns
each retained record a positive weight. Selection responds to the calibration targets rather than
being drawn at random, so the retained sample is informed by the quantities the dataset must
reproduce. The gates make the retained-record count an explicit optimization variable, so one
framework can produce a compact national dataset or a larger subnational one, while soft and hard
concentration controls bound how large individual weights can grow. Because the optimization that
selects records also calibrates them, the reduced dataset continues to match its targets.

We implement the method within \populace{}, PolicyEngine's pipeline for microsimulation dataset
construction, and present a proof of concept on its current target surface. The comparison holds the
candidate universe, the target set, and the record budget fixed, and varies only how records are
chosen, across three samplers: informed $L_0$ selection, random sampling followed by gradient-descent
reweighting, and survey-weight sampling, which draws records with probability proportional to a prior
calibration's weights (the unbiased Hansen--Hurwitz scheme). All three fit weights with the same
calibrator, so the experiment isolates the selection step rather than the calibration. Informed $L_0$
selection reaches much lower out-of-sample error than random sampling under aggressive compression, where
a random draw is too small to span the targets: at a 2{,}000-record budget its mean absolute relative
error is 53\% against random sampling's 2{,}293\%. The methods converge as the record budget grows, and
above roughly 5{,}000 records random sampling becomes the more accurate of the two; survey-weight
sampling is the least accurate throughout. The method's distinctive value is operational rather than a
uniform accuracy gain: it sets the dataset size, geographic emphasis, and weight concentration through
explicit parameters in one optimization, and it removes the seed-to-seed variation that can make a small
random draw fail. We report these results as a proof of concept on a national and state target surface,
and leave the larger build-and-prune and subnational settings the controls are designed for to future
work.
\end{abstract}

\noindent\textbf{Keywords:} microsimulation, survey calibration, subsampling, $L_0$ regularization,
subnational analysis
