\appendix

\section{Optimization hyperparameters}
\label{app:hyperparameters}

Table~\ref{tab:hyperparameters_full} lists the hyperparameters of the $L_0$ optimization with their
roles. The gate parameters follow the Hard Concrete construction of \citet{louizos2018}. The
sparsity penalty $\lambda_{L_0}$ and the epoch count are set per build to reach a target dataset
size and are reported with each run.

\begin{table}[ht]
\centering
{\tablefont
\begin{tabular}{lll}
\toprule
Parameter & Value & Role \\
\midrule
Gate temperature $\beta$ & 0.35 & Sharpness of the 0/1 gate transition \\
Left stretch $\gamma$ & $-0.1$ & Enables exact-zero gates after clipping \\
Right stretch $\zeta$ & 1.1 & Enables exact-one gates after clipping \\
Initial keep probability & 0.999 & Records start nearly fully active \\
Weight jitter SD & 0.05 & Log-space noise on weights at initialization \\
Logit jitter SD & 0.01 & Log-space noise on gate logits at initialization \\
$\lambda_{L_2}$ & $10^{-12}$ & Weight-magnitude penalty \\
Learning rate & 0.15 & Adam optimizer step size \\
$\lambda_{L_0}$ & \tbc & Sparsity penalty, set to reach the target dataset size \\
Epochs & \tbc & Training iterations \\
\bottomrule
\end{tabular}
}
\caption{Hyperparameters for the $L_0$ optimization. Gate parameters follow \citet{louizos2018}.
Source: the \texttt{l0-python} Hard Concrete implementation used by \populace{}.}
\label{tab:hyperparameters_full}
\end{table}

\section{Sample-size presets}
\label{app:presets}

\input{tables/presets}

\section{Calibration targets}
\label{app:targets}

This study calibrates to a prioritized subset of the targets the pipeline can construct. The subset
is reported here in full, so the empirical claims can be read against the exact target system used
rather than against a pipeline-wide inventory. The subset was chosen for \tbc[selection rationale,
for example coverage of major tax and transfer aggregates across geographic levels], and it is not
presented as a complete or maximal target set. Other targets the pipeline can build are out of scope
for this study.

\tbc[target families, types, geographic levels, and counts for the prioritized subset]

\section{Algorithm pseudocode}
\label{app:algorithm}

Algorithm~\ref{alg:l0} presents the $L_0$-regularized calibration procedure.

\begin{algorithm}[ht]
\caption{$L_0$-regularized calibration with Hard Concrete gates}
\label{alg:l0}
\begin{algorithmic}[1]
\Require Calibration matrix $\mathbf{M} \in \R^{m \times n}$, targets $\mathbf{t} \in \R^m$, initial weights $\mathbf{w}_0 \in \R^n$
\Require Hyperparameters: $\lambda_{L_0}$, $\lambda_{L_2}$, $\beta$, $\gamma$, $\zeta$, learning rate $\eta$, epochs $E$
\Ensure Calibrated sparse weight vector $\hat{\mathbf{w}} \in \R^n$

\State Initialize $\log w_i \gets \log w_{0,i} + \mathcal{N}(0, 0.05^2)$ for all $i$
\State Initialize $\log \alpha_i \gets \text{logit}(0.999) + \mathcal{N}(0, 0.01^2)$ for all $i$
\State Initialize Adam optimizer with parameters $\{\log w_i, \log \alpha_i\}$ and learning rate $\eta$

\For{epoch $= 1$ to $E$}
    \State \textbf{Sample Hard Concrete gates (training):}
    \For{$i = 1$ to $n$}
        \State $u_i \sim \text{Uniform}(\epsilon, 1-\epsilon)$
        \State $\bar{s}_i \gets \sigma\!\left(\frac{\log u_i - \log(1-u_i) + \log \alpha_i}{\beta}\right)$
        \State $s_i \gets \bar{s}_i(\zeta - \gamma) + \gamma$
        \State $z_i \gets \min(1, \max(0, s_i))$
    \EndFor
    \State $w_i^{\text{eff}} \gets \exp(\log w_i) \cdot z_i$ for all $i$
    \State $\hat{t}_j \gets \sum_i M_{ji} \cdot w_i^{\text{eff}}$ for all $j$
    \State $\mathcal{L}_{\text{cal}} \gets \frac{1}{m}\sum_{j=1}^{m}\left(\frac{\hat{t}_j - t_j}{|t_j|}\right)^2$
    \State $\mathcal{L}_{L_0} \gets \sum_{i=1}^{n} \sigma\!\left(\log \alpha_i - \beta \log \frac{-\gamma}{\zeta}\right)$
    \State $\mathcal{L}_{L_2} \gets \sum_{i=1}^{n} w_i^2$
    \State $\mathcal{L} \gets \mathcal{L}_{\text{cal}} + \lambda_{L_0} \mathcal{L}_{L_0} + \lambda_{L_2} \mathcal{L}_{L_2}$
    \State Backpropagate $\nabla_{\log w, \log \alpha} \mathcal{L}$
    \State Adam step
\EndFor

\State \textbf{Deterministic inference:}
\For{$i = 1$ to $n$}
    \State $z_i^{\text{det}} \gets \min\!\left(1, \max\!\left(0,\; \sigma(\log \alpha_i)(\zeta - \gamma) + \gamma\right)\right)$
    \State $\hat{w}_i \gets \exp(\log w_i) \cdot z_i^{\text{det}}$
\EndFor
\State \Return $\hat{\mathbf{w}}$
\end{algorithmic}
\end{algorithm}

\section{Dataset assembly details}
\label{app:assembly}

After optimization the fitted weight vector is mapped back to record form and used to assemble the
deployable dataset. The assembly step keeps the active records, reconstructs their person and
tax-unit memberships, derives geography from the stored assignment, and recomputes
geography-dependent quantities. Two details matter for fidelity. Geography is derived from the same
assignment used to build the calibration matrix, so the assembled dataset matches the universe the
optimizer saw. Take-up draws are regenerated with the same deterministic seeds used during matrix
construction, so take-up-dependent targets stay consistent between the calibration problem and the
assembled dataset.
