\section{Conclusion}
\label{sec:conclusion}

This paper studies $L_0$ regularization as a way to subsample a large microsimulation dataset down to
a usable size. The problem arises because a pipeline built for fidelity combines many sources and
adds record-level variation, which produces more candidate records than a deployable dataset can
hold. The reduction to a fixed budget is a sampling choice, and the paper treats it as one.

The method uses Hard Concrete gates to select records and fit their weights in one optimization, with
selection driven by the calibration targets. That makes the retained-record count an explicit control
and keeps the reduced dataset calibrated to its targets. We compare the method against matched-budget
baselines that share its calibrator, and report the frontier between retained records, Populace's
production calibration loss, and weight concentration.

The current experiment evaluates the production-style question directly: every materialized target in the
current Populace surface is fit and scored, including congressional-district targets. The result is a
sampling frontier, and it is a negative accuracy result for the current selector. Random sampling followed
by gradient reweighting is the strongest full-surface baseline on the production loss; informed $L_0$ plus
post-selection refit improves on the raw gated weights and becomes competitive at larger budgets, but does
not overtake random + reweight. That finding is still useful because it identifies the next engineering
target: improve target-informed selection without increasing weight concentration.

The contribution is therefore twofold: a target-informed sampling method, and an open pipeline,
\populace{}, that makes the method a configuration choice other projects can reuse.
Section~\ref{sec:future_work} sets out the build-large-then-prune extensions and targeted robustness
comparisons that follow from the full-surface run.
