\section{Future work}
\label{sec:future_work}

This study moves the proof of concept onto \populace{}'s current full target surface, including
congressional-district targets. The next empirical step is to turn the matched probe into a frontier by
sweeping the normalized sparsity share across retained counts. Holdout panels should remain separate
robustness checks that ask narrower
questions: which target families or geographies generalize when withheld, which targets dominate the loss,
and how sensitive the result is to the production target weights and cap.

A related thread varies the penalties the headline run deliberately holds fixed. The reported experiments
set $\lambda_{L_2}=0$ and leave the weight cap off, so the comparison isolates the effect of the $L_0$
gates on sparsification; this leaves the concentration controls as a clean axis to study on their own.
Three experiments follow. First, evaluate the convex $L_1$ selector of Section~\ref{sec:l1_background}
head-to-head with $L_0$ on the same surface: because a single $L_1$ penalty couples how many records
survive with how much the survivors shrink, we expect it to be a weaker selector than the $L_0$ gates,
and running it would show whether that coupling actually costs it. Second, sweep the soft concentration
penalty $\lambda_{L_2}$ and the hard \texttt{max\_weight\_ratio} cap against $\lambda_{L_0}$. Third, use
that sweep to trace the effective-sample-size against accuracy trade-off, quantifying how much calibration
fit a build gives up to bound weight concentration.

A second thread is the build-large-then-prune regime the controls are designed for, in which a pipeline
assembles a candidate universe far larger than it can ship---hundreds of thousands or millions of records
rather than a compact survey file---and prunes it to a deployable budget under the calibration targets.
The current three-year support file is a step in that direction. More aggressive support expansion is
where target-informed selection has its clearest opportunity to justify its cost: a random draw from a
tight budget is least likely to span a demanding target system, so a selector trained on the targets has
the most to add.

The full-surface design also clarifies which classical comparators are worth adding. Survey-weight
(probability-proportional-to-size) sampling is the natural calibrate-then-reduce counterpart to random +
reweight and belongs in the next frontier as a literature comparator, with the caveat that it selects
records by the population mass they represent rather than by their fit to the targets. Raking, GREG,
balanced sampling, and combinatorial optimization remain relevant reference methods, but not all are
natural baselines for a heterogeneous
32{,}633-target fiscal surface. The appropriate next comparison is on the simpler categorical-margin
subsets where their assumptions hold cleanly, in the spirit of \citet{tanton2014co}'s comparison of
generalized regression with combinatorial optimisation for small-area reweighting, while the production
frontier continues to use the Populace loss over the complete surface.
