\section{Introduction}
\label{sec:introduction}

Tax-benefit microsimulation models apply policy rules to household microdata to estimate fiscal and
distributional effects. At the national level, that usually means starting from a survey such as the
Current Population Survey (CPS), improving measured incomes and program participation, and adjusting
weights so the dataset reproduces known aggregates. Subnational work is harder. Analysts often want
estimates for states, congressional districts, or local areas, but the underlying survey was not
designed to support all of those geographies at once.

That gap matters in practice, because many reforms are proposed, administered, or debated below the
national level. A state tax proposal needs state-specific incomes, filing patterns, and benefit
participation. District-level analysis needs those same outcomes to aggregate correctly within each
district while staying consistent with state and national totals. A usable subnational dataset
therefore has to satisfy a hierarchical calibration problem rather than a single national one.

One way to meet that demand is to build a dataset that carries as much of the relevant variation as
possible. A pipeline can combine several surveys and administrative files, impute the variables that
any single source lacks, and attach the geographic detail that local analysis needs. Each of these
steps enriches the records, and some add records. The result is a candidate dataset rich enough to
represent the variation the targets describe, and large enough that it becomes expensive to store,
calibrate, and simulate. A file with millions of active records supports
detailed subnational work but is slow to run; a much smaller file is easier to ship, but only if the
loss in fidelity is acceptable.

The candidate dataset therefore has to be reduced to a size that can be shipped and simulated, and
this paper treats that reduction as a sampling problem: given the large candidate universe and a
fixed record budget, which records should the final dataset keep, and what weight should each kept
record carry? The simplest answer is to draw a random subset
and reweight it to the targets. We study an alternative in which the selection itself is informed by
the targets.

The method is $L_0$ regularization with the Hard Concrete relaxation \citep{louizos2018}. Each
candidate record receives a gate that the optimizer can drive toward zero or one, and the expected
number of open gates enters the objective directly. Minimizing calibration error and the gate count
together selects a subset of records and fits their weights in one optimization. The retained-record
count becomes a quantity the optimizer controls rather than a fixed draw, and two concentration
controls (a soft penalty and a hard per-record cap) limit how concentrated the fitted weights can
become. In practical terms, one framework can target a compact national dataset or a larger subnational
dataset, at a chosen record budget, with weights kept inside a usable range.

We situate this work in \populace{} \citep{populace2026}, PolicyEngine's pipeline for microsimulation
dataset construction. \populace{} passes a single weighted data structure through a sequence of
modular stages---source loading, imputation, geographic assignment, target construction, and
calibration---each implemented as a separate package operating on that shared structure. Because the
stages are modular, the data sources, the imputation model, the geographic assignment, and the
calibration method are interchangeable components rather than fixed code, and the calibration step
studied here is one such component. The paper describes the pipeline at the level needed to follow the
calibration step, and then describes the configuration used here.

This paper is a proof of concept on \populace{}'s current full target surface: it asks whether
$L_0$ selection with Hard Concrete gates can produce a sparse, calibrated dataset on the targets
\populace{} assembles today, including the congressional-district surface that motivates the build-big,
then-prune workflow. Local-area and subnational calibration are therefore part of the target surface being
fit, while full production release engineering remains outside the scope of the proof of concept.

The empirical question is whether informed selection earns its added complexity. We ask three
things. First, on the actual \populace{} loss over the full target surface, does informed $L_0$ selection
or its post-$L_0$ refit reproduce the targets more accurately than dense calibration and sampling
baselines under the same optimizer budget? Second, what do supplemental raw-error diagnostics reveal about
the tail of the target distribution? Third, does the framework give usable control over the size of the
output and the concentration of the fitted weights? The current full-surface probe gives a constructive
answer: the raw gated $L_0$ weights are not good enough by themselves, but the support selected by the
gates becomes more accurate than matched random support and slightly lower-loss than the 1{,}500-epoch
dense no-$L_0$ run after an ordinary calibration refit.

The rest of the paper follows that structure. Section~\ref{sec:background} places the work in the
literature on spatial microsimulation, survey calibration, and sparse selection.
Section~\ref{sec:data} describes the base microdata, the \populace{} pipeline, and the
administrative targets. Section~\ref{sec:methodology} presents the calibration method and the
sampling experiment design. Section~\ref{sec:results} reports the comparison against the sampling
baselines and the behaviour of the size, geography, and weight controls. Section~\ref{sec:discussion}
interprets those results and discusses their limits, and Section~\ref{sec:conclusion} concludes.
