\section{Methodology}
\label{sec:methodology}

This section describes the calibration method that selects and weights records, and then the design
of the experiment that evaluates the method as a sampler.

\subsection{The shared calibrator}

The calibration matrix $\mathbf{M} \in \R^{m \times n}$ maps $n$ candidate records to $m$ targets.
Entry $M_{ji}$ is the contribution of candidate $i$ to target $j$: an indicator or count for count
targets, and a simulated tax or benefit value for dollar targets. The matrix is built from
\policyengine{} simulations evaluated under the policy rules that apply to each record's assigned
geography, and is stored in sparse form. Given a weight vector $\mathbf{w} \in \R^n$, the estimate of
target $j$ is
\begin{equation}
    \hat{t}_j = \sum_{i=1}^{n} M_{ji}\, w_i.
    \label{eq:estimate}
\end{equation}

The methods compared in this study fit weights with the same calibrator, the \texttt{calibrate}
routine in \populace{}. It minimizes a capped, weighted mean absolute percentage error (capped weighted
MAPE) of the estimates against the targets,
\begin{equation}
    \mathcal{L}_{\mathrm{cal}}(\mathbf{w}) =
    \frac{\sum_{j=1}^{m} \omega_j \min\!\left(\left|\dfrac{\hat{t}_j - t_j}{s_j}\right|,\, c\right)}
         {\sum_{j=1}^{m} \omega_j},
    \label{eq:loss_cal}
\end{equation}
where $s_j = \max(|t_j|, 1)$ scales each target by its own magnitude, with a floor of one unit so a
zero-valued target stays well defined; $c$ caps the contribution of any single hard-to-fit target, so
one badly conditioned target cannot dominate the gradient, and is set to the production value $c = 1$ in
the runs reported here; and $\omega_j$ are
per-target weights, normalised by their sum so only their relative magnitudes matter. The error is
relative, so a one per cent miss on a small target and on a large one count the same. The weights are
parameterized in log space, $w_i = \exp(\theta_i)$, so the fitted weights stay positive; an Adam
optimizer \citep{kingma2015} implemented in PyTorch \citep{pytorch2019} minimizes the loss, and the
total weight is held to the input population. On a fixed set of records this calibrator answers a
calibration question: it finds weights that match the targets. Dense no-$L_0$, post-$L_0$ refit, and
random + reweight use it unchanged on different supports; informed $L_0$ extends it with a selection
term.

The per-target weights $\omega_j$ in the runs reported here follow \populace{}'s production US-fiscal
weighting, computed through the same code path the production US build uses rather than a separate
reimplementation. The weighting is built in four steps. Each target is first assigned to one of two
value bases from its measure metadata: a count basis (indicator, enrollment, recipient, and
return-count measures) or an amount basis (dollar measures). Within a basis, a target's raw
weight is proportional to $\max(|t_j|, 1)^{1/2}$, the square root of its own magnitude, so a larger
aggregate carries more weight but sublinearly (a target a hundred times larger receives about ten times
the weight), and these raw weights are normalised to mean one inside each basis. The two bases are then
rescaled to contribute equal total weight, so the far more numerous dollar cells do not swamp the count
targets. A final step sets the mean weight to one. Because the loss divides by $\sum_j \omega_j$, only
the relative weights enter the objective and their absolute scale does not.

\subsection{Selection and weighting as one optimization}

Informed $L_0$ sampling adds two terms to the shared calibrator that turn weight fitting into record
selection. Each candidate $i$ carries a Hard Concrete gate $z_i \in [0, 1]$ \citep{louizos2018}, the
gated estimate becomes $\hat{t}_j = \sum_i M_{ji} w_i z_i$, and the optimizer minimizes
\begin{equation}
    \mathcal{L}(\mathbf{w}, \boldsymbol{\alpha}) =
    \mathcal{L}_{\mathrm{cal}}(\mathbf{w}, \mathbf{z}) +
    \lambda_{\mathrm{share}}\frac{1}{n}\sum_{i=1}^{n} \bar{z}_i +
    \lambda_{L_2} \frac{1}{n} \sum_{i=1}^{n} \left(\frac{w_i}{w_{0,i}}\right)^2.
    \label{eq:loss}
\end{equation}
The first term is the capped weighted MAPE of Equation~\ref{eq:loss_cal}, now evaluated on the gated
weights $w_i z_i$. The second term is the $L_0$ penalty and sets the sample size: $\bar{z}_i = \Pr(z_i \neq 0)$ is the
expected activation of gate $i$ (Equation~\ref{eq:l0penalty}), so $\sum_i \bar{z}_i$ is the expected number of open gates, the
expected retained-record count, and $\lambda_{L_0}$ sets how aggressively the optimizer prunes. In the
full-surface probe we report $\lambda_{L_0}$ through a normalized penalty share,
$\lambda_{\mathrm{share}}\sum_i\bar{z}_i/n$, so the sparsity price is comparable when the candidate
record count changes. The raw coefficient passed to the optimizer is therefore
$\lambda_{L_0}=\lambda_{\mathrm{share}}/n$. The third term is a soft concentration penalty: $\lambda_{L_2}$ multiplies the mean squared ratio of each
fitted weight to its initial weight $w_{0,i}$, which discourages the optimizer from carrying the fit on
a few heavily inflated records. It applies to informed $L_0$ only; the dense and random baselines run the
shared calibrator without any selection or concentration term.

Read as a sampler, the calibration term keeps the retained sample faithful to the targets, the $L_0$
penalty sets the sample size, and the $L_2$ penalty governs weight concentration. The concentration
term matters because an $L_0$ penalty on its own can reach a sparse solution that is still unusable: the
optimizer can match the targets by placing very large weights on a few retained records. Both
concentration controls act on the ratio of each fitted weight to its initial weight, $w_i / w_{0,i}$.
The $L_2$ term is a soft penalty on the mean square of that ratio that discourages large inflations
smoothly, and it is the natural control for tracing the accuracy-concentration trade-off.
\texttt{max\_weight\_ratio} is a hard per-record cap on the same ratio: no fitted weight may exceed a
fixed multiple of that record's initial weight, clamped after every optimizer step. The soft penalty
shapes the whole weight distribution during optimization; the cap bounds the single largest weight.
Size and concentration are therefore set by separate controls: $\lambda_{L_0}$ sets how many records
remain, and the $L_2$ penalty and \texttt{max\_weight\_ratio} can fix how concentrated their weights may
become. The headline full-surface probe leaves the cap off and sets $\lambda_{L_2}=0$, so the reported
accuracy comparison is the pure-calibration result. Tightening either control is a natural robustness panel:
it bounds how much population a single record can carry, at some cost to calibration fit. Appendix~\ref{app:hyperparameters} lists the
full configuration, and Appendix~\ref{app:algorithm} gives the optimization loop as
Algorithm~\ref{alg:l0}.

The gates and the weights are learned together: the gate decides whether a record is in the sample,
and the weight decides how much it counts. Because both are fit against the same calibration loss,
selection is informed by the targets: a record survives when keeping it helps match a target that
would otherwise be missed. This is the sense in which the method is a target-informed sampler rather
than a reweighting of a fixed random draw.

\subsection{From fitted weights to a dataset}

After optimization the gates are evaluated deterministically, so the retained-record count is read
from the solution rather than chosen by a post-hoc cutoff. The retained records and their weights are
assembled into a dataset for \policyengine{}. Appendix~\ref{app:assembly} summarizes the assembly
step, which matters operationally but is not the object of the experiment.

\subsection{Sampling experiment design}
\label{sec:experiment_design}

The experiment evaluates whether informed selection produces a better dataset than the alternative
samplers at the same record budget. The literature offers more possible comparators than can be run
cleanly on the full mixed target surface: raking-based workflows are natural on categorical margins,
balanced sampling is designed for fixed balancing variables, and combinatorial optimisation is
discrete and costly at production scale. The headline comparison therefore keeps the candidate
universe, target surface, positivity restriction, and calibration loss fixed, and varies only the way
records are selected and, for the post-selection arms, refit. From one candidate universe and one target
set, the matched full-surface probe compares five method arms: informed $L_0$ selection, informed $L_0$
selection followed by an ordinary calibration refit on the selected records, dense no-$L_0$ calibration on
the full candidate universe, random sampling followed by gradient reweighting, and a no-refit random
sample of dense calibrated weights scaled back to total mass. The run arms are:

\begin{itemize}
    \item \textbf{Informed $L_0$ sampling with Hard Concrete gates.} The shared calibrator with the
    gate and concentration terms above selects records and fits their weights jointly at a chosen
    budget, set through $\lambda_{L_0}$.
    \item \textbf{Informed $L_0$ + refit.} The same selected records are kept, but the gates are removed
    and the shared calibrator refits ordinary dense weights on that retained subset, initialized from the
    informed $L_0$ weights. This post-$L_0$ refit isolates the value of the selected subset from the
    particular gated weights returned by the joint optimization.
    \item \textbf{Dense no-$L_0$ calibration.} The shared calibrator fits positive weights on the full
    337{,}704-record candidate universe, with gates off and no sparsity or concentration penalty. This is
    the finite-optimization dense benchmark.
    \item \textbf{Random sampling with gradient-descent reweighting.} A random subset of the candidate
    universe of the same size is drawn, then the shared calibrator fits its weights to the same targets
    without the gate or concentration terms. This is the reduce-first, calibrate-after baseline.
    \item \textbf{Dense random scaled sample.} Dense no-$L_0$ weights are fit once on the full universe;
    a uniform random subset of the matched size is retained; the retained dense weights are then scaled so
    their total equals the dense total, with no post-sampling refit. This tests whether dense calibration
    alone can be made sparse by random thinning and mass scaling.
\end{itemize}

This design does not claim that raking, GREG, balanced sampling, or combinatorial optimisation are
irrelevant in general. They remain the reference methods for simpler margin surfaces, classical
calibration, target-balanced survey designs, and discrete synthetic-population construction. The
empirical comparison below focuses on the methods that can be applied to the full Populace target
surface under the same scoring loss and that were run in the real-data probe.

Holding the candidate universe and the target set fixed isolates the effect of how records are
chosen. Every method starts from the same candidate frame with its weights reset to a uniform prior, so
each record's initial weight $w_{0,i}$ is one shared constant. The reported probe uses
$\lambda_{\mathrm{share}}=0.8$, which equals raw $\lambda_{L_0}=2.37\times10^{-6}$ for the 337{,}704
candidate records and retains 57{,}240 records. The post-$L_0$ refit, dense no-$L_0$, and random +
reweight baselines each use a 1{,}500-epoch optimizer budget; the sparse baselines use the same
57{,}240-record count. Sweeps across penalties and concentration controls are the next
robustness panel rather than part of the headline evidence here.

\subsection{Full-surface scoring}
\label{sec:oos}

The production motivation is to construct a deployable dataset that fits the full target surface 
\populace{} currently assembles. The headline experiment therefore fits and scores every materialized 
target, including validation-only families and congressional-district targets. In the run reported here, 
37{,}053 Ledger facts compile to 32{,}633 materialized calibration targets on 337{,}704 candidate 
household records. The reported objective is the same capped, weighted calibration loss in 
Equation~\ref{eq:loss_cal}, evaluated on the final retained weights and excluding the $L_0$ and $L_2$ 
penalties. This is the frontier an analyst would use when choosing a publishable record budget for 
the actual \populace{} build.

Generalization to structurally different targets is a separate question this proof of concept does not
test. A meaningful holdout here would withhold whole target families rather than random target rows,
because targets nest within a family (a national total is the sum of its state cells) and a random split
would leak, with a held-out cell nearly determined by its retained siblings; we leave that family-level
holdout robustness to future work (Section~\ref{sec:future_work}).

\subsection{Evaluation metrics}
\label{sec:metrics}

Each run reports the metrics in Table~\ref{tab:metrics} for the scored targets. They fall into two
groups: accuracy measures, which ask how closely the weighted
estimates reproduce the targets, and representativeness measures, which ask at what cost in weight
concentration and compute that accuracy is bought.

\begin{table}[H]
\centering
{\tablefont
\begin{tabular}{p{0.24\textwidth}p{0.34\textwidth}p{0.30\textwidth}}
\toprule
Metric & Definition & Why reported \\
\midrule
Populace objective loss & Equation~\ref{eq:loss_cal}: capped, target-weighted relative error, penalty-free & Headline target-fit metric; this is the loss the production calibrator optimizes \\
Median ARE & Median absolute relative error $|\hat{t}_j - t_j| / |t_j|$ over scored targets & Supplemental accuracy diagnostic, robust to the near-zero-denominator tail \\
Mean and max ARE & Mean and maximum of the same per-target errors & Supplemental, tail-sensitive diagnostics \\
Effective sample size & $\mathrm{ESS} = (\sum_i w_i)^2 / \sum_i w_i^2$ and the implied design effect & A sampler can fit the targets while concentrating population mass on a few records, so ESS is a primary result, not a footnote \\
Retained count & Non-zero record count & Sample size \\
Max weight & Largest fitted weight & Weight concentration \\
Runtime & Wall-clock time & Compute cost \\
\bottomrule
\end{tabular}
}
\caption{Metrics reported for each run. Accuracy is led by the Populace objective loss, with raw ARE
metrics reported as supplemental diagnostics; effective sample size measures the weight concentration that
accuracy is achieved at.}
\label{tab:metrics}
\end{table}

Errors are reported by geographic level as well as in aggregate, because a sampler can match national
totals while missing local ones.

A small number of targets have denominators so small that a single record can swing their relative error
past 100 per cent. We identify these structurally rather than by an arbitrary cutoff: target $j$ is
denominator-degenerate when its value is smaller than its identifiability floor
$\max_i |M_{ji}|\, w_{0,i}$, the largest contribution any single record makes at its initial weight. For
such a target the absolute relative error reflects integer placement noise rather than calibration
quality. Rather than winsorize or trim the error distribution, we name these targets in a one-time
audit and report a targeted-removal sensitivity (the mean recomputed with exactly those named targets
dropped) beside the full mean, so the effect of the degenerate targets is visible and attributable.
Target counts are read from each run's manifest.
