\documentclass[11pt]{article}

\usepackage{ijm}
\input{macros}

\title{$L_0$ regularization for subnational microsimulation calibration}

\author{
    María Juaristi\thanks{PolicyEngine. Corresponding author: maria@policyengine.org} \and
    Nikhil Woodruff\footnotemark[1] \and
    Ben Ogorek\footnotemark[1] \and
    Max Ghenis\footnotemark[1]
}
\date{}

\begin{document}

\maketitle

\input{sections/abstract}
\input{sections/introduction}
\input{sections/background}
\input{sections/data}
\input{sections/methodology}
\input{sections/results}
\input{sections/discussion}
\input{sections/conclusion}

% --- Required end-matter statements ---
\section*{Conflict of interest}
All authors are affiliated with PolicyEngine, the nonprofit organization that develops \populace{} and
the \texttt{l0-python} package evaluated in this paper. The authors have no other competing interests.

\section*{Funding}
This work was supported by PolicyEngine, a 501(c)(3) nonprofit organization.

\section*{Data and code availability}
The paper and experiment code are at \url{https://github.com/PolicyEngine/l0-paper}. The construction
and calibration pipeline is implemented in \populace{}, PolicyEngine's microsimulation data stack,
open source at \url{https://github.com/PolicyEngine/populace}; earlier prototype code in the archived
\texttt{microplex} and \texttt{microplex-us} repositories is retained only as a migration reference.
The administrative targets are source-backed facts from PolicyEngine Ledger, open source at
\url{https://github.com/PolicyEngine/arch-data}.
The \texttt{l0-python} PyTorch package that implements the Hard Concrete optimizer is available at
\url{https://github.com/PolicyEngine/l0-python}. Calibrated datasets are hosted on HuggingFace at
\texttt{policyengine/policyengine-us-data}. The current reproduction workflow relies on public code
and generated data artifacts.

\section*{Use of generative AI}
The authors used Claude (Anthropic) and Codex (OpenAI) for code assistance and manuscript drafting. All technical
content, methodology, and analysis were designed and validated by the authors.

\bibliographystyle{plainnat}
\bibliography{./bibliography/references}

\input{sections/appendix}

\end{document}
